Distinguishing Spin-Aligned and Isotropic Black Hole Populations With Gravitational Waves

### 2017-04-12 paper/AlignedIsotropicGW.tex
Removed bold first sentences in figures.

%
\begin{figure}
\centering
\includegraphics[width=\textwidth]{../plots/posterior_on_isotropic_fraction.png}
\caption{\textbf{Fraction of the BBH population coming from an
    isotropic distribution under a mixture model.} The dotted line
  shows the flat prior on the fraction of BBHs coming from an
  isotropic distribution, $f_i$, under the mixture model. The 3 red
  lines show the posterior on $f_i$ after O1 with our various
  assumptions regarding BH spin magnitudes.  The solid line shows the
  posterior assuming that all BHs have their spin magnitude drawn from
  the ``flat'' distribution. The dashed line assumes the ``high'' BH
  spin magnitude distribution $p(a) = 2a$. The dot-dash line assumes
  the ``low'' distribution $p(a) = 2(1-a)$.  We see that for a wide
  range of assumptions regarding BH spin magnitudes, the fraction
  coming from an isotropic distribution $f_i$ peaks at 1.}
\label{fig:mixture_fraction_posterior}
\end{figure}
%

@@

%
\begin{figure}
\centering
\includegraphics[width=\textwidth]{../plots/sigma_v_alpha.png}
\caption{\textbf{Effect of small spins on evidence ratio of aligned
    against isotropic models.} The blue line shows the evidence ratio
  (plotted as the equivalent sigma) between a model where all systems
  are aligned, versus one where all systems are from an isotropic
  distribution as a function of the power law $\alpha$ corresponding
  to Equation~\ref{eq:lowspinalpha}.  The top axis shows the mean spin
  magnitude $\bar{a}$ which this $\alpha$ corresponds to. We see that
  for mean spin magnitudes $\lesssim 0.2$ we find no evidence for
  either distribution over the other.}
\label{fig:smallspinsalpha}
\end{figure}
%

>>>>

%
\begin{figure}
\centering
\includegraphics[width=\textwidth]{../plots/posterior_on_isotropic_fraction.png}
\caption{Fraction of the BBH population coming from an isotropic
  distribution under a mixture model. The dotted line shows the flat
  prior on the fraction of BBHs coming from an isotropic distribution,
  $f_i$, under the mixture model. The 3 red lines show the posterior
  on $f_i$ after O1 with our various assumptions regarding BH spin
  magnitudes.  The solid line shows the posterior assuming that all
  BHs have their spin magnitude drawn from the ``flat''
  distribution. The dashed line assumes the ``high'' BH spin magnitude
  distribution $p(a) = 2a$. The dot-dash line assumes the ``low''
  distribution $p(a) = 2(1-a)$.  We see that for a wide range of
  assumptions regarding BH spin magnitudes, the fraction coming from
  an isotropic distribution $f_i$ peaks at 1.}
\label{fig:mixture_fraction_posterior}
\end{figure}
%

@@

%
\begin{figure}
\centering
\includegraphics[width=\textwidth]{../plots/sigma_v_alpha.png}
\caption{Effect of small spins on evidence ratio of aligned against
  isotropic models. The blue line shows the evidence ratio (plotted as
  the equivalent sigma) between a model where all systems are aligned,
  versus one where all systems are from an isotropic distribution as a
  function of the power law $\alpha$ corresponding to
  Equation~\ref{eq:lowspinalpha}.  The top axis shows the mean spin
  magnitude $\bar{a}$ which this $\alpha$ corresponds to. We see that
  for mean spin magnitudes $\lesssim 0.2$ we find no evidence for
  either distribution over the other.}
\label{fig:smallspinsalpha}
\end{figure}
%
